ps4_models

### 2020-10-30 bi-model.Rmd
asd

@@

total_rows <- nrow(reduced_data)
table(reduced_data$vote_2020)
table(reduced_data$age_group)
levels(reduced_data$education)
levels(reduced_data$gender)
levels(reduced_data$race_ethnicity)
reduced_data <- reduced_data %>% select(vote_2020, age_group, education, gender, 
                                        race_ethnicity, state)
```
```{r}
set.seed(50)
shuffle_indices <- sample(total_rows)
data <- reduced_data[shuffle_indices,]
boundary <- as.integer(total_rows*0.95)

@@

```{r}
testing <- data[boundary:total_rows,]
testing$vote_num <- if_else(testing$vote_2020 == "Donald Trump", 0, 1 )
# probability <- model %>% add_predicted_draws(newdata = testing)

# training <- data[0:boundary,]
# training$vote_num <- if_else(training$vote_2020 == "Donald Trump", 0, 1 )

@@

testing <- testing %>% mutate(acc = probs==vote_num)

@@

```{r}
pred_post <- cleaned_post

@@

```{r}
table(if_else(probability>=0.5,"Joe Biden",
                                  "Donald Trump" ))
```

>>>>

reduced_data$vote_enum <- if_else(reduced_data$vote_2020 == "Donald Trump", 0, 1 )

@@

total_rows <- nrow(reduced_data)
table(reduced_data$vote_2020)
table(reduced_data$age_group)
levels(reduced_data$education)
levels(reduced_data$gender)
levels(reduced_data$race_ethnicity)
reduced_data <- reduced_data %>% select(vote_2020,vote_enum, age_group, education, gender, 
                                        race_ethnicity, state)
```
```{r}
set.seed(50)
shuffle_indices <- sample(total_rows)
data <- reduced_data[shuffle_indices,]
boundary <- as.integer(total_rows*0.95)

@@

```{r}
testing <- data[boundary:total_rows,]
# probability <- model %>% add_predicted_draws(newdata = testing)

# training <- data[0:boundary,]
# training$vote_num <- if_else(training$vote_2020 == "Donald Trump", 1, 0 )

@@

testing <- testing %>% mutate(acc = probs==vote_enum)

@@

```{r}
set.seed(101)
pred_post <- cleaned_post

@@

```{r}
table(if_else(probability<=0.5,"Joe Biden",
                                  "Donald Trump" ))

summary(model)
```
